\documentclass[fleqn, onecolumn]{article}
\usepackage{amsmath}
%\usepackage[landscape]{geometry}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{fullpage}
%\usepackage{hyperref}
%\usepackage{listings}
%\setlength{\parindent}{0in}

\begin{document}
\title{LEDA Memo: 8 Bit Sampling of LWA Data}
\date{}
\author{Terry Filiba}
\maketitle

\section{Summary}
In order to determine the suitability of an 8 bit ADC for sampling LWA data, we analyzed data taken every 15 minutes over a 24 hour period from 6 LWA dual pol stands. 
The data was captured using the currently available 12 bit ADCs.

Analysis of the data showed that at least 97\% of the samples lie within the range $[-128,128)$. 
Therefore, without adjusting any gains there would be $< 3\%$ error due to saturation using an 8 bit ADC.
If the ADC gain is set so that the RMS is $20$, the error rate of the ADC gets even lower. 
With the sampled data rescaled, saturation only occurs in $<0.001\%$ of the samples using an 8 bit ADC (an error rate of $10^{-5}$). 

\begin{table}[h]
\input{table.tex}
\end{table}

\section{Histograms}
The rest of the memo contains histograms of the data from each stand-pol. 
Each histogram is shown in linear and log scale, to highlight the peakedness and short tails of each distribution. 
The blue bars highlight the samples that could be represented with 8 bits without gain adjustment. 
The yellow bars show the samples that would not saturate if the gain was adjusted so that the RMS is $20$.
The log plots of the data emphasize the short tails in the histogram, showing that adjusting the gain will be an effective way to reduce the saturation rate. 
\input{plots.tex}

\end{document}